Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-04-04 manuscript/manuscript.tex
Restructured introduction in manuscript

\citet{Uieda2016} developed a forward gravity model based on tesseroids with homogeneous densities using the GLQ approximation method.
It has been originally implemented through command line programs written in C programming language.
However, it has been ultimately ported to Python and included in the open-source library Fatiando a Terra \citep{Uieda2013} for geophysical modelling and inversion.

\citet{Ku1977} proved that the GLQ becomes less accurate when the computation point is closer to the tesseroid or for smaller GLQ order. 
Although the model developed by \citet{Uieda2016} uses a second order GLQ, it ensures the accuracy implementing a modified version of the adaptive discretization of \citet{Li2011}.
It consist in splitting the tesseroid into smaller ones when a certain distance-size ratio is lower than a predefined value ($D$) that controls the accuracy of the computation. 
\citet{Uieda2016} have also objectively obtained standard values of $D$ for gravity potential, gradients and tensor components comparing the numerical model with the fields generated by a spherical shell, which constitutes a special case of the volume integrals that has analytical solution \citep{LaFehr1991, Mikuska2006, Grombein2013}\todo{citar mas??}.

>>>>

\citet{Uieda2016} developed a forward gravity model based on tesseroids with 
homogeneous densities using the GLQ approximation method.
It has been originally implemented through command line programs written in C 
programming language.
However, it has been ultimately ported to Python and included in the 
open-source library Fatiando a Terra \citep{Uieda2013} for geophysical 
modelling and inversion.
\todo{hace falta aclarar sobre el software de leo?}

\citet{Ku1977} proved that the GLQ becomes less accurate when the computation 
point is closer to the tesseroid or for smaller GLQ order.
Although the model developed by \citet{Uieda2016} uses a second order GLQ, it 
ensures the accuracy implementing a modified version of the adaptive 
discretization of \citet{Li2011}.
It consist in splitting the tesseroid into smaller ones when a certain 
distance-size ratio is lower than a predefined value ($D$) that controls the 
accuracy of the computation.
\citet{Uieda2016} have also objectively obtained standard values of $D$ for 
gravity potential, gradients and tensor components comparing the numerical 
model with the fields generated by a spherical shell, which constitutes a 
special case of the volume integrals that has analytical solution 
\citep{LaFehr1991, Mikuska2006, Grombein2013}
\todo{citar mas??}.
